{RandomRationalPoints} package for \emph{Macaulay2}

### 2020-12-18 FastLinAlg/Paper/RandomRationalPoints.tex
RandomRationalPoints.tex checked for typos

%\vspace{1em}
As again, we can have the following additional options:
\begin{description}
\item[\tt Strategy => Symbol] This specifies which strategy to use when calling {\tt randomPoints}.
\item[\tt Homogeneous => Boolean] This is passed in calls to {\tt randomPoints}.
\item[\tt Verbose => Boolean] This turns on or off verbose output (see \Cref{findANonZeroMinor})
\item[\tt MinorPointAttempts => ZZ] This controls how many points at which to check the rank of the matrix.
\end{description}

@@

One use for this function can be in showing a certain rings are $R1$ (regular in codimension $1$).
Consider the following example which is $R1$ where computing the dimension of the singular locus takes around $30$ seconds as there are $15500$ minors of size $4 \times 4$ in the associated $7 \times 12$ Jacobian matrix.  However, we can use this function to quickly find interesting minors.
\begin{example}

>>>>

%\vspace{1em}
As again, we can have the following additional options:
\begin{description}
\item[\tt Strategy => Symbol] This specifies which strategy to use when calling {\tt randomPoints}.
\item[\tt Homogeneous => Boolean] This is passed in calls to {\tt randomPoints}.
\item[\tt Verbose => Boolean] This turns on or off verbose output (see \Cref{findANonZeroMinor}).
\item[\tt MinorPointAttempts => ZZ] This controls how many points at which to check the rank of the matrix.
\end{description}

@@

One use for this function can be in showing that certain rings are $(R_1)$ (regular in codimension $1$).
Consider the following example which is $(R_1)$ where computing the dimension of the singular locus takes around $30$ seconds as there are $15500$ minors of size $4 \times 4$ in the associated $7 \times 12$ Jacobian matrix.  However, we can use this function to quickly find interesting minors.
\begin{example}
